Changelog

### 2021-05-20 changelog.tex
Updates from Overleaf

\section{Introduction}

\end{document}

>>>>

\section{Introduction}
(1). Fuzzing – need stronger motivation

(2). Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.

(3). Can you extend your research (especially the quantification part) to include other side channel signals?

(4). A bits vs. Q bits. Lower bounds?
Improve the presentation
Make the comparison more meaningful

(5). iid assumption – does it fit your research on side-channel?

(6). Some feedback I gave before your defense.
\end{document}
